Project Notes

### 2020-04-17 notes/notes.tex
Notes: update 13/04/2020
Notes: update ≤17/04/2020

\paragraph{10/04/2020}
\begin{itemize}
\item
Start formalising the encoding for states and runtime for Node targets.

@@

>>>>

\paragraph{10/04/2020}
\begin{itemize}
\item
Start formalising the encoding for states and runtime for Node targets.
\end{itemize}

\paragraph{13/04/2020}
\begin{itemize}
\item
Fix type signature for React event handler -- extract the 
camelCase keys from \texttt{React.DOMAttributes} and infer
the type of event (e.g. MouseEvent from `onClick') to correctly
type the event handler.
\end{itemize}

\paragraph{16/04/2020}
\begin{itemize}
\item
Experiment with what code should be generated
for explicit cancellation using the Calculator example.

\item
Verify (through experimenting in code) that affine channel
usage cannot be violated by introducing long for-loops
in backend to simulate delay in Calculator example. 
This will be better addressed by supporting Promises
in the future.

@@

\paragraph{17/04/2020}
\begin{itemize}
\item
Exploring the theory for reasoning about global types
specific for web services generation.
\end{itemize}
